%-------------------------
% Resume in Latex
% Author : Milind  Pawar
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article} % reduced font size to fit on one page

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\evensidemargin}{-0.45in}
\addtolength{\textwidth}{0.9in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://devopsguys.in//}{\Large Milind Pawar}} & Email :  \href{mailto:hello@cv.com}{milindpawar5555@gmail.com}\\
  \href{https://www.linkedin.com/in/mpawar1/}{LinkedIn} \textbar{} \href{https://github.com/milindpawar007/}{GitHub} & Mobile : 667-770-2727 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland Baltimore County}{Baltimore, MD}
      {(MS in Information Systems and Management); GPA: 4.0/4.0}{Aug 2019 - May 2021}
    \resumeSubheading
      {University of Pune}{Pune, India}
      {(Bachelor of Engineering in Information Technology); GPA: 3.6/4.0}{Aug 2011 - May 2015}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{}{\textbf{Languages}: JavaScript, TypeScript, Python, HTML5, CSS3, SQL, NoSQL}
    \resumeSubItem{}{\textbf{Frameworks / Libraries}: React.js, Redux, Node.js, Next.js, SPFx, Tailwind CSS, Express.js, Bootstrap}
    \resumeSubItem{}{\textbf{Tools \& Platforms}: Adobe Target, AWS, Jenkins, Git, Docker, Azure, Power Automate, GraphQL, REST API, Postman, Jira, VS Code}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {LTIMindtree}{Dallas, TX}
    {Senior Software Engineer}{Jul 2024 -- Present}
 
   \textbf{Project: Banner Health – Modern Intranet Development with React \& SPFx}
\begin{itemize}
  \item Built scalable React.js SPFx web parts for SharePoint  using TypeScript, Microsoft Graph API, and PnP JS.
  \item Migrated legacy components to functional React with Hooks, improving performance and maintainability.
  \item Implemented Context API for state management and optimized rendering with lazy loading and memoization.
  \item Developed responsive, pixel-perfect UI from Figma; collaborated with designers to ensure accessibility.
  \item Integrated REST APIs and Power Automate workflows to automate business logic and enhance interactivity.
\end{itemize}

\textbf{Project: Home Depot – Experimentation and Personalization (A/B Testing)}
\begin{itemize}
  \item Developed scalable React.js applications integrated with RESTful and GraphQL APIs for dynamic personalization.
  \item Led migration of legacy codebase to React with Redux, increasing development efficiency by 40\%.
  \item Executed A/B tests using Adobe Target; drove a 15\% uplift in conversions and 25\% boost in retention.
  \item Built CI/CD pipelines using Jenkins and GitHub Actions; reduced deployment errors by 35\%.
  \item Deployed containerized apps using Docker on AWS; ensured 99.9\% uptime with monitoring and alerting.
\end{itemize}

  \resumeSubheading
    {Index Analytics LLC}{Baltimore, MD}
    {Software Engineer Intern}{Jan 2021 -- May 2021}
    \resumeItemListStart
      \resumeItem{}{Built dynamic web portal using \textbf{React.js}, \textbf{ASP.NET}, \textbf{Node.js}, deployed on \textbf{AWS EC2/S3} with IAM-secured roles.}
      \resumeItem{}{Implemented SSR for SEO, enabled localization, and managed component library with Storybook.}
      \resumeItem{}{Partnered with analytics team to visualize reporting with real-time chart rendering using D3.js.}
      \resumeItem{}{Integrated role-based authentication and session management using JWT and secure cookies.}
    \resumeItemListEnd
\vspace{1\baselineskip} %
  \resumeSubheading
    {Keys LLC}{Baltimore, MD}
    {Software Engineer Intern}{May 2020 -- Dec 2020}
    \resumeItemListStart
      \resumeItem{}{Maintained hotel booking platform using \textbf{C\#}, \textbf{ASP.NET},Node integrated with Azure Blob Storage for asset hosting.}
      \resumeItem{}{Built scalable RESTful APIs and optimized backend queries, reducing latency by 30\%.}
      \resumeItem{}{Wrote comprehensive test suites using \textbf{Jest}, \textbf{Mocha}, integrated into Git hooks for pre-push validation.}
      \resumeItem{}{Improved UI/UX across booking flows, reduced cart abandonment by simplifying interactions.}
    \resumeItemListEnd
\vspace{1\baselineskip} %
  \resumeSubheading
    {Data Link Consultancy (Vodafone India)}{Pune, India}
    {Software Engineer}{Dec 2016 -- Apr 2018}
    \resumeItemListStart
  \item Supported internal web application development in Agile teams using modern full-stack technologies.
  \item Built reusable and scalable UI components in React.js to deliver responsive front-end experiences.
  \item Developed Login and Management modules using HTML5, CSS3, JavaScript, and React.js.
  \item Integrated AWS services and helped troubleshoot backend issues related to MySQL and server config.
  \item Created RESTful APIs using Node.js to streamline front-end/backend communication via JSON and AJAX.
  \item Contributed to multiple POCs demonstrating integration of React front-end with Node.js backend.
  \item Practiced Git version control and followed team collaboration standards for codebase management.
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------CERTIFICATIONS------------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{}{Microsoft Certified: Azure Fundamentals}
    \resumeSubItem{}{Microsoft Certified: Azure Data Fundamentals}
  \resumeSubHeadingListEnd

\end{document}
